Is It Possible to Steal Money Through USB-C?

### 2020-12-23 WOOT/Files/background.tex
note possible copy
changing USB citation from 0x to x0 i.e. USB 2.0's citation is usb20 instead of usb02, and added some background

\section{Background}
\label{sec:background}
\noindent\outline{USB Standard}\\
\outline{Terminology}\\
\outline{USB1.0}\\
\outline{USB2.0}\\
\outline{USB3.0}\\
\outline{USB-C}\\
\outline{Arduino USB Stack/Linux 2.0 Gadget Driver}\\

>>>>

\section{Background}
\label{sec:background}
\noindent\outline{USB Standard}\\
We first introduce the development of USB specification and emphasize the key points adopted in our work.

\noindent\outline{USB1.x}\\
Proposed in 1996, USB 1.0\cite{usb10} was developed to provide an unified interface and thus reducing the cost of re-configuring the software.

USB1.x\cite{usb10}\cite{usb11} provided two data transfer rates which are Low Speed (1.5 Mbit/s) and Full Speed (12 MBit/s). At this point, due to the transfer limit, it only supports limited kinds of devices like keyboard, mice, etc.

\noindent\outline{USB2.0}\\
In 2000, USB2.0\cite{usb20} was released.
\outline{USB3.0}\\
\outline{USB-C}\\
\outline{Arduino USB Stack/Linux 2.0 Gadget Driver}\\

### 2020-12-23 WOOT/Files/related_work.tex
changing USB citation from 0x to x0 i.e. USB 2.0's citation is usb20 instead of usb02, and added some background

In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.
\subsection{USB Attack Security}
\hongyi{DO NOT COPY!}\textcolor{red}{USB 1.0\cite{usb01} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}.} USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s). Before USB 2.0 was released in 2000 and widely used, USB attacks are limited to human layer error attacks, \cite{se}, \cite{goverment}, \cite{atkvec}, \cite{ueerreallydo}, e.g, throwing a bad USB device on purpose, are in order to damage host through plugging in a peripheral by trust default.

@@

As our best knowledge, attacks based on USB 3.0\cite{usb03} have not been discovered. In this work, we focus on attack based on USB 3.0 in the layer of transport\cite{sok}, which use the USB protocol to control the host or inject malicious command to the host connected with Type-C\cite{typec}, and streal the data trough it.

>>>>

In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.
\subsection{USB Attack Security}
\hongyi{DO NOT COPY!}\textcolor{red}{USB 1.0\cite{usb10} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}.} USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s). Before USB 2.0 was released in 2000 and widely used, USB attacks are limited to human layer error attacks, \cite{se}, \cite{goverment}, \cite{atkvec}, \cite{ueerreallydo}, e.g, throwing a bad USB device on purpose, are in order to damage host through plugging in a peripheral by trust default.

@@

As our best knowledge, attacks based on USB 3.0\cite{usb30} have not been discovered. In this work, we focus on attack based on USB 3.0 in the layer of transport\cite{sok}, which use the USB protocol to control the host or inject malicious command to the host connected with Type-C\cite{typec}, and streal the data trough it.
